### 2023-12-20 manuscript.tex
test references [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/90f28e1fb1cc918aed174bcec72e566f71336385.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/90f28e1fb1cc918aed174bcec72e566f71336385/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/7279249918

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/a11eee09f9c75888c4714ff01fb405f467edc32f/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/a11eee09f9c75888c4714ff01fb405f467edc32f}{MMV-Lab/im2im-paper@a11eee0}
on December 20, 2023.

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/90f28e1fb1cc918aed174bcec72e566f71336385/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/90f28e1fb1cc918aed174bcec72e566f71336385}{MMV-Lab/im2im-paper@90f28e1}
on December 20, 2023.
